Detecting Facial Expressions in Professional Tennis Matches

### 2017-09-18 Report06-12.Rmd
Edited plots and explanations

This stacked bar chart, Figure \@ref(fig:ICFigs) Plot c, allows consideration of the interaction between two image attributes. We are able to see that the background being the Logo Wall and the angle of Player Shoulder Height is common to the highest amount of faces. There are also no images that were taken at an upward angle with the background of the court.

@@

plots <- arrangeGrob(MosaicShotangle, MosaicSit, sbbgshot, sbbgsit,
             nrow=2, ncol=2)

g <- ggplotGrob(sbbgshot + theme(legend.position="bottom"))$grobs
legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
lheight <- sum(legend$height)

grid.arrange(plots, legend,
        ncol = 1,
        heights = unit.c(unit(1, "npc") - lheight, lheight))
```

@@

aminFaces %>%
  filter(type=="Manual") %>% 
  select(glasses) %>%
  table -> ManGlasses

aminFaces %>% filter(matchesManual) -> afm

>>>>

This stacked bar chart, Figure \@ref(fig:ICFigs) Plot c, allows consideration of the interaction between two image attributes. We are able to see that the background being the Logo Wall and the angle of Level is common to the highest amount of faces. There are also no images that were taken at an upward angle with the background of the court.

@@

g1 <- ggplotGrob(sbbgshot + theme(legend.position="bottom"))$grobs
legend1 <- g1[[which(sapply(g1, function(x) x$name) == "guide-box")]]
lheight1 <- sum(legend1$height)

plots1 <- arrangeGrob(sbbgshot, sbbgsit, ncol=2)
plots1 <- arrangeGrob(plots1, legend1, nrow=2, heights = unit.c(unit(1, "npc") - lheight1, lheight1))

g2 <- ggplotGrob(MosaicShotangle + theme(legend.position="bottom"))$grobs
legend2 <- g2[[which(sapply(g2, function(x) x$name) == "guide-box")]]
lheight2 <- sum(legend2$height)

plots2 <- arrangeGrob(MosaicShotangle, MosaicSit, ncol=2)
plots2 <- arrangeGrob(plots2, legend2, nrow=2, heights = unit.c(unit(1, "npc") - lheight2, lheight2))

grid.arrange(plots1, plots2, nrow=2)

@@

ManFaces %>% count(glasses) %>%
  tally() -> ManGlasses

aminFaces %>% filter(matchesManual==TRUE) -> afm
